Data Preparation

### 2019-01-11 Data Preparation.Rmd
minor change

```{r stemming d_description}
stem_with_dictionary <- function(data) data %>%
                                         left_join(dictionary, by = "word") %>%
                                         rename(word_original = word,
                                                word = word_stem)

>>>>

```{r stemming data sets}
stem_with_dictionary <- function(data) data %>%
                                         left_join(dictionary, by = "word") %>%
                                         rename(word_original = word,
                                                word = word_stem)
